Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-06-29 paper.tex
Fix lead author email footnote
Add subsections to Applications section

\author{M.\ Brett Deaton}
\affiliation{Joint Institute for Nuclear Astrophysics,
  Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics,
  North Carolina State University, Raleigh, NC 27695, USA}
\email{mbdeaton@ncsu.edu}

@@

\subsection{Emission Spectra}
\label{ssec:spectra}
The merger models are described in \cite{fouc2015-m1_nsbh, fouc2016-m1_nsns}.
Something like this is presented in \cite[Figs.~10-11]{pere2014-nu_wind};
compare.]
\todo{compute $H^r(\mu;\varepsilon)$ in nsns and nsbh}
\todo{compute $\langle \varepsilon \rangle(\mu)$}

>>>>

\author{M.\ Brett Deaton}
\email{mbdeaton@ncsu.edu}
\affiliation{Joint Institute for Nuclear Astrophysics,
  Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics,
  North Carolina State University, Raleigh, NC 27695, USA}

@@

\subsection{Understanding Emission Spectra}
\label{ssec:spectra}
In this section, we use ray tracing's ability to track ``where the neutrinos
are coming from'' to understand the features in the emission distributions
presented in the code tests.

The merger models are described in \cite{fouc2015-m1_nsbh, fouc2016-m1_nsns}.
Something like this is presented in \cite[Figs.~10-11]{pere2014-nu_wind};
compare.]
\todo{compute $H^r(\mu;\varepsilon)$ in nsns and nsbh}
\todo{compute $\langle \varepsilon \rangle(\mu)$}

\subsection{Neutrino Self-Interaction Potential}
\label{ssec:V_nunu}
In this section we present $V_{\nu\nu,0}$ along one test trajectory in the NSNS
model, and show that including elastic scattering makes a qualitative
difference in the character of the flavor evolution.

\subsection{Neutrino Annihilation Integral}
\label{ssec:q_nunu}
In this section we calculate $q_{\nu\bar{\nu}}$ at a representative point
in the funnel of the NSNS configuration and show that including scattering makes
a difference (or not) in our estimate of the power available to drive a jet.
